ChIP-seq example

### 2018-10-18 analysis/chipseq.Rmd
wflow_publish("chipseq.Rmd")

```{r plot-smash-estimates}
nbreaks <- 80
p <- create.chipseq.plot(bppos/1e6,counts,res$est,(peaks$start+peaks$end)/2e6,
                         nbreaks) +
  scale_x_continuous(limits = c(0.88,1.02),breaks = seq(0.88,1.02,0.02)) +
  scale_y_continuous(limits = c(-1,9),breaks = seq(0,8,2))
```

>>>>

```{r plot-smash-estimates, fig.height=4, fig.width=8}
create.chipseq.plot(bppos/1e6,counts,res$est,(peaks$start + peaks$end)/2e6,
                    nbreaks = 80) +
  scale_x_continuous(limits = c(0.88,1.02),breaks = seq(0.88,1.02,0.02)) +
  scale_y_continuous(limits = c(-1,9),breaks = seq(0,8,2))
```
